### 2015-04-28 evaluation.tex
update in the text

We can see that, in general, \whoop reports (many) more races than \corral. This is expected because \whoop over-approximates the original driver for soundness: if a race exists, the tool will report it (assuming tool and model correctness), but \whoop can, and does, report false races. On the other hand, \corral reports only real races, but does that under pre-defined bounds. It is worthwhile to note that a common problem for \corral (especially when analyzing drivers) is loop coverage. To deal with this we enable the over-approximation described in~\cite{lal2014powering}. This can potentially lead \corral to report false positives, but we have not seen this in practice.

>>>>

We can see that, in general, \whoop reports (many) more races than \corral. This is expected because \whoop over-approximates the original driver for soundness: if a race exists, the tool will report it (assuming tool and model correctness), but \whoop can, and does, report false races. On the contrary, \corral reports only real races, but does that under pre-defined bounds and thus can miss races.

### 2015-04-28 whoop.tex
update
update in the text

\whoop is a sound but potentially imprecise static data race analyzer.  While developers do appreciate soundness, it is more important to ensure they are not overwhelmed by countless reports of false bugs.  Hence, to improve precision, we enable an external precise bug-finder for concurrent programs to be plugged into \whoop. The race-related information generated by \whoop can then be used to accelerate the bug-finder.  Currently, we support \corral~\cite{lal2012corral}, a state-of-the-art scalable bug-finder used by Microsoft to analyze Windows device drivers. \corral accepts Boogie IVL and hence it was easy to integrate into our toolchain (see Figure~\ref{fig:whoop} -- C). Our technique, though, is general and capable of accelerating any arbitrary bug-finder for concurrent programs.

\corral is a symbolic bounded verifier for Boogie IVL that uses the Z3 SMT solver to statically reason about program behaviors. It checks for violations of provided assertions, and reports a precise counterexample if an assertion violation is found. \corral performs bounded exploration of a concurrent program in two steps. First, given a bound on the number of allowed context-switches, the concurrent program is appropriately \emph{sequentialized}, and the generated sequential version preserves reachable states of the original concurrent program~\cite{popl2011-eqr,cav2009-lqr,cavLalR08}. Then, \corral attempts to prove bounded (in terms of the number of loop iterations and recursion depth) sequential reachability of a bug in a goal-directed, lazy fashion to postpone state space explosion when analyzing a large program. It performs two abstractions to achieve this: (i) variable abstraction, where it attempts to identify a minimal set of shared variables that have to be precisely tracked in order to discharge all assertions; and (ii) stratified inlining, where it attempts to inline procedures on-demand as they are required for proving program assertions.

@@

Note that our instrumentation conveniently tolerates most benign races, as it does not report a write-write race if two write accesses update the same shared memory location with the same value.  We introduce the instrumentation as a precise feasibility check for the potential data races that \whoop reports.

>>>>

\whoop is a sound but potentially imprecise static data race analyzer.  While developers do appreciate soundness, it is more important to ensure they are not overwhelmed by countless reports of false bugs.  Hence, to improve precision, we enable an external precise bug-finder for concurrent programs to be plugged into \whoop. The race-related information generated by \whoop can then be used to accelerate the bug-finder.  Currently, we support \corral~\cite{lal2012corral, lal2014powering}, a state-of-the-art scalable bug-finder used by Microsoft to analyze Windows device drivers. \corral accepts Boogie IVL and hence it was easy to integrate into our toolchain (see Figure~\ref{fig:whoop} -- C). Our technique, though, is general and capable of accelerating any arbitrary bug-finder for concurrent programs.

\corral is a symbolic bounded verifier for Boogie IVL that uses the Z3 SMT solver to statically reason about program behaviors. It checks for violations of provided assertions, and reports a precise counterexample if an assertion violation is found. \corral performs bounded exploration of a concurrent program in two steps. First, given a bound on the number of allowed context-switches, the concurrent program is appropriately \emph{sequentialized}, and the generated sequential version preserves reachable states of the original concurrent program~\cite{popl2011-eqr,cav2009-lqr,cavLalR08}. Then, \corral attempts to prove bounded (in terms of the number of loop iterations and recursion depth) sequential reachability of a bug in a goal-directed, lazy fashion to postpone state space explosion when analyzing a large program. It performs two abstractions to achieve this: (i) variable abstraction, where it attempts to identify a minimal set of shared variables that have to be precisely tracked in order to discharge all assertions; and (ii) stratified inlining, where it attempts to inline procedures on-demand as they are required for proving program assertions. \corral also employs sophisticated strategies for improving loop coverage, these are described in more detail in~\cite{lal2014powering}.

@@

Note that our instrumentation conveniently tolerates most benign races, as it does not report a write-write race if two write accesses update the same shared memory location with the same value.  An advantage of this instrumentation is that it can be used as a precise feasibility check for the potential data races that \whoop reports.
